\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-08 paper/draft.tex
Add comments from OSDI reviews

We now evaluate \sys on an existing set of \unix pipelines found in the wild and written by non-experts.

@@

\heading{Results}
\sys's parallelism is set to $16\times$, as many of these pipelines are relatively long (\S\ref{eval}, Parallelism).
Their input was generated by multiplying their original input several times, enough to reach 10GB.
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for all \todo{30} pipelines. We use the pipeline index to refer to them in both plots and discussion.
%% (\nv{Pipelines are referred by number, in both the plot and the discussion below.})
Average speedup is \todo{$6.02\times$}, median is $6.48\times$, and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},
We do not include three pipelines that take less than 0.1 seconds to execute because they only output the first line of their input using \ttt{head}.

@@

>>>>

We now evaluate \sys on an existing set of \unix pipelines found in the wild and \todo{written by non-experts}.
% \kk{OSDI reviewer asked how do you know if they are non-experts.}

@@

\heading{Results}
\sys's parallelism is set to $16\times$, as many of these pipelines are relatively long (\S\ref{eval}, Parallelism).
Their input was generated by \todo{multiplying their original input several times, enough to reach 10GB.}
% \kk{eurosys: One OSDI reviewer didn't like how this is phrased. Can we change that?}
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for all \todo{30} pipelines. We use the pipeline index to refer to them in both plots and discussion.
%% (\nv{Pipelines are referred by number, in both the plot and the discussion below.})
Average speedup is \todo{$6.02\times$}, median is $6.48\times$, and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},
We do not include three pipelines that take less than 0.1 seconds to execute because they only output the first line of their input using \ttt{head}.

@@

\kk{Mention something about Nebula (as an OSDI reviewer asked for.)}
